MLExplain

### 2018-05-24 paper.tex
Rajouté une référence pour js_of_ocaml

To interpret OCaml code, we need to parse it. However, our compiler does not
allow us to use the standard library nor an external one.

>>>>

To interpret OCaml code, we need to parse it. However, our compiler does not
allow us to use the standard library nor an external one. Fortunately,
JSExplain itself did not trace the parsing process. That is why we have been
able to separate totally the parser from the interpreter and use another
compiler to compile it. The figure \ref{fig:archi} describes the architecture
of the whole application.

The parser is compiled with
\emph{js\_of\_ocaml} \cite{DBLP:journals/spe/VouillonB14}, the compiler of the
project \emph{Ocsigen}.
